### 2009-12-01 doc/tech_doc/a-rex/arex_tech_doc.tex
Getting rid of symbolic links (they don't work on Windows!), correcting Makefiles

For information about supported LRMSes and their specific features
and configuration options please read dedicated documentation~\cite{backends-arc1}.

@@

\bibliography{grid}
\end{document}

>>>>

For information about supported LRMSes and their specific features
and configuration options please read dedicated documentation~\cite{arc1-backends}.

@@

\bibliography{grid,nordugrid}
\end{document}
